Yeast RNA-seq 48 sample simulation study: Bimodal alternative, 2000 DE genes

### 2018-08-15 datasets/RNA-Seq/yeast-simulation-bimodalalternative.Rmd
Don't repeat null settings for varying alternative settings

# results files that will be generated
resfile_n5 <- file.path(resdir, "yeastII-results-null5.rds")
resfile_n10 <- file.path(resdir, "yeastII-results-null10.rds")
resfile_d5 <- file.path(resdir, "yeastII-results-de5.rds")
resfile_d10 <- file.path(resdir, "yeastII-results-de10.rds")
resfile_d5_uw <- file.path(resdir, "yeastIIU-results-de5.rds")
resfile_d10_uw <- file.path(resdir, "yeastIIU-results-de10.rds")

resfile_n5_uninfCov <- file.path(resdir, "yeastII-results-null5-uninfCov.rds")
resfile_n10_uninfCov <- file.path(resdir, "yeastII-results-null10-uninfCov.rds")
resfile_d5_uninfCov <- file.path(resdir, "yeastII-results-de5-uninfCov.rds")
resfile_d10_uninfCov <- file.path(resdir, "yeastII-results-de10-uninfCov.rds")
resfile_d5_uninfCov_uw <- file.path(resdir, "yeastIIU-results-de5-uninfCov.rds")
resfile_d10_uninfCov_uw <- file.path(resdir, "yeastIIU-results-de10-uninfCov.rds")

@@

Here we'll repeat the above, but for a DE comparison 5 versus 5 Snf2 samples,
where the groups are selected randomly and 2000 DE genes are added. 
This will be done for 100 random splits.

>>>>

# results files that will be generated
resfile_d5 <- file.path(resdir, "yeastII-results-de5.rds")
resfile_d10 <- file.path(resdir, "yeastII-results-de10.rds")
resfile_d5_uw <- file.path(resdir, "yeastIIU-results-de5.rds")
resfile_d10_uw <- file.path(resdir, "yeastIIU-results-de10.rds")

resfile_d5_uninfCov <- file.path(resdir, "yeastII-results-de5-uninfCov.rds")
resfile_d10_uninfCov <- file.path(resdir, "yeastII-results-de10-uninfCov.rds")
resfile_d5_uninfCov_uw <- file.path(resdir, "yeastIIU-results-de5-uninfCov.rds")
resfile_d10_uninfCov_uw <- file.path(resdir, "yeastIIU-results-de10-uninfCov.rds")

@@

Here we'll carry out a DE comparison 5 versus 5 Snf2 samples,
where the groups are selected randomly and 2000 DE genes are added. 
This will be done for 100 random splits. Note that we do not need to run null
comparisons, since these are done in `yeast-simulation.Rmd`, and the only
difference here is that we use a different under the alternative.
